---
title: "Lab 7 Multiple Choice Exercises"
author: "Tessa McDonnel"
date: "9/7/2017"
output: html_document
---


#### Test assumption exercises for two sample t-test


--- type:NormalExercise lang:r xp:100 skills:1 key:79a37231a2
## Assumptions for a two sample t-test


Before conducting a two sample t-test, we need to make sure that our data meets these 2 conditions:

* the observations are independent
* the quantitative variable is normally distributed (or sample sizes are greater than 30 in each group)


It is reasonable to assume that the student's number of absent days are not related to each other, so the observations are independent.

In this exercise, you will be checking the second condition for the `absent` variable in `schooldays`.


*** =instructions
- Type `library(mosaic)` to load the *mosaic* package into your workspace.
- Use the `favstats()` function to examine summary statistics of `absent` by `race`. Recall the syntax: `favstats(dataset$quant_var ~ dataset$categ_var)`
- Use the `hist()` function on the `absent` variable in `schooldays`.
- Click the 'Submit Answer' button and look at the R output. Does this distribution look normal to you?


*** =hint
For the second instruction, use the format: `favstats(dataset$quant_var ~ dataset$categ_var)` with specified data set and variables. Remember, the quantitative variable is `absent` and the categorical variable is `race`.

To create a histogram use the format: `hist(dataset$variable)`
*** =pre_exercise_code
```{r}
library(HSAUR)
library(mosaic)
```

*** =sample_code
```{r}
# Load the mosaic package 

# Use favstats() to examine summary statistics of absent days by race


# Create a histogram of number of absent days


```

*** =solution
```{r}
# Load the mosaic package 
library(mosaic)

# Use favstats() to examine summary statistics of absent days by race
favstats(schooldays$absent ~ schooldays$race)


# Create a histogram of number of absent days
hist(schooldays$absent)


```

*** =sct
```{r}
test_student_typed("library(mosaic)",  not_typed_msg =  "Type `library(mosaic)` to load the mosaic package.")


test_student_typed("favstats(schooldays$absent ~ schooldays$race)", not_typed_msg = "Make sure you follow the format: `favstats(dataset$quant_var ~ dataset$categ_var)` with the correct data set (`schooldays`), quant_var (`absent`) and categ_var (`race`).")

test_function("hist", args = "x", incorrect_msg = "Make sure you follow the format `hist(dataset$variable)` with the `schooldays` data set and `absent` variable.")

success_msg("Nice job. Look at the R output, do you think this data meets the second condition?")

```




--- type:MultipleChoiceExercise lang:r xp:50 skills:1 key:5a24579348
## Quick check: t-test assumptions
The *Plots* panel contains the histogram of the number of absent days from the last exercise. 

The `favstats()` results from the last exercise are stored in an object called `results`; in your R console type `results` to view these.

Question: Does the `absent` days variable from `schooldays` follow the second condition?

*Remember, the second condition is met if a histogram of the variable looks approximately symmetric and bell-shaped OR if sample sizes in each group are greater than 30.*

*** =instructions
- No, because the histogram is right-skewed and the sample sizes for each group are too small.
- Yes, the histogram is right-skewed but the sample sizes are over 30. 
- No, because the sample sizes for each group are too small.
- Yes, the histogram looks approximately normal even though the sample sizes are too small.

*** =hint
Since the tail of the distribution is on the right side, it is right-skewed. Type `results` to view the sample sizes in each racial group.

*** =pre_exercise_code
```{r}
library(HSAUR)
library(mosaic)
results <- favstats(schooldays$absent ~ schooldays$race)
hist(schooldays$absent)
```

*** =sct
```{r}
msg_bad <- "That is not correct. The distribution is very right skewed but the sample sizes are large."
msg_success <- "Exactly!"
test_mc(correct = 2, feedback_msgs = c(msg_bad, msg_success, msg_bad, msg_bad))
```


****

#### Test assumption exercise for paired t-test


--- type:NormalExercise lang:r xp:100 skills:1 key:34994f646a
## Assumptions for paired t-test
 
 
Before we conduct the paired t-test, we need to make sure our data follows these assumptions:

* independent observations
* difference in weights are normally distributed (or large sample size)
 
The independence assumption is met because it is reasonable to assume that the *patients* are independent of one another.

In this exercise, you will be checking the second condition for the the `diffwt` variable in the `anorexia` data set.


*Remember, the second condition is met if a histogram of the variable looks approximately symmetric and bell-shaped OR if the sample size is larger than 30.*


*** =instructions
- Type `library(mosaic)` to load the *mosaic* package into your workspace.
- Use `favstats()` to explore your new variable `diffwt` from the `anorexia` data set.
- Use the `hist()` on `diffwt` from the `anorexia` data set.
- Click the 'Submit Answer' button and check the output. Are the assumptions met?
*** =hint

- Use the format `favstats(dataset$variable)` for the second instruction.
- To create a histogram use the format: `hist(dataset$variable)`.
- Remember we are using the data set called `anorexia`.
*** =pre_exercise_code
```{r}
library(mosaic)
library(MASS)
anorexia$diffwt <- anorexia$Postwt - anorexia$Prewt

```

*** =sample_code
```{r}
# Load the mosaic package 

# Explore diffwt with the favstats() function

# Create a histogram of diffwt


```

*** =solution
```{r}
# Load the mosaic package 
library(mosaic)

# Explore diffwt with the favstats() function
favstats(anorexia$diffwt)

# Create a histogram of diffwt
hist(anorexia$diffwt)


```

*** =sct
```{r}
test_student_typed("library(mosaic)",  not_typed_msg =  "Type `library(mosaic)` to load the mosaic package.")

test_function("favstats", args = "x", incorrect_msg = "Make sure you follow the format `favstats(dataset$variable)` with the `anorexia` data set and `diffwt` variable.")


test_function("hist", args = "x", incorrect_msg = "Make sure you follow the format `hist(dataset$variable)` to create a histogram of the `diffwt` variable from the `anorexia` data set.")

success_msg("Good! Now look at the output. We can see from the histogram that the distribution of the differences is not perfectly normal HOWEVER the sample size is over 30 so the conditions are satisfied.")
```

****

#### Test assumption exercise for ANOVA


--- type:NormalExercise lang:r xp:100 skills:1 key:8a95e5e62d
## Assumptions of ANOVA

Before conducting an ANOVA test, we need to make sure that our data meets these 2 assumptions:

* the observations are independent
* the quantitative variable is normally distributed (or sample sizes in each group are greater than 30)


It is reasonable to assume that patients are not related to each other, so the observations are independent.

In this exercise, you will be checking the second condition for the `Postwt` variable in the `anorexia` data set.

*The second condition is met if a histogram of the variable looks approximately symmetric and bell-shaped OR if the sample size in each group is larger than 30*
*** =instructions
- Type `library(mosaic)` to load the *mosaic* package into your workspace.
- Use the `favstats()` function to examine summary statistics of post weights `Postwt` by treatment `Treat` in the `anorexia` data set.
- Use the `hist()` function to obtain a histogram of `Postwt`.
- Click the 'Submit Answer' button and check the output. Are the assumptions met?


*** =hint
- For the second instruction, use the format: `favstats(dataset$quant_var ~ dataset$categ_var)` with the correct data set (`anorexia`), quantitative variable (`Postwt`) and categorical variable (`Treat`).
- To create a histogram, use the format: `hist(dataset$variable)` with the correct data set and variable.

*** =pre_exercise_code
```{r}
library(MASS)
library(mosaic)
```

*** =sample_code
```{r}
# load the mosaic package 

# Explore relationship between treatment and post weights. Recall the syntax: favstats(dataset$quant_var ~ dataset$categ_var)


# Create a histogram of post-treatment weights


```

*** =solution
```{r}
# load the mosaic package 
library(mosaic)

# Explore relationship between treatment and post weights. Recall the syntax: favstats(dataset$quant_var ~ dataset$categ_var)
favstats(anorexia$Postwt ~ anorexia$Treat)


# Create a histogram of post-treatment weights
hist(anorexia$Postwt)

```

*** =sct
```{r}
test_student_typed("favstats(anorexia$Postwt ~ anorexia$Treat)", not_typed_msg = "Make sure you follow the format: `favstats(dataset$quant_var ~ dataset$categ_var)` with the correct data set (`anorexia`), quant_var (`Postwt`) and categ_var (`Treat`).")

test_function("hist", args = "x", incorrect_msg = "Make sure you follow the format `hist(dataset$variable)` with the `anorexia` data set and `Postwt` variable.")

success_msg("The post-treatment weights appear to be slightly skewed and the sample sizes in each group is less than 30, so the second condition is not satisfied. However, we will continue to demonstrate how to execute ANOVA in R.")
```








