---
title: "Lab 7 Multiple Choice Exercises"
author: "Tessa McDonnel"
date: "9/7/2017"
output: html_document
---


\begin{verbatim}

--- type:MultipleChoiceExercise lang:r xp:50 skills:1 key:5a24579348
## Quick check 1
The *Plots* panel contains the histogram of the number of absent days from the last exercise. 

The `favstats()` results from the last exercise are stored in an object called `results`; in your R console type `results` to view these.

Question: Does the `absent` days variable from `schooldays` follow the second condition?

*Remember, the second condition is met if a histogram of the variable looks approximately symmetric and bell-shaped OR if sample sizes in each group are greater than 30.*
*** =instructions
- No, because the histogram is right-skewed and the sample sizes for each group are too small.
- Yes, the histogram is right-skewed but the sample sizes are over 30. 
- No, because the sample sizes for each group are too small.
- Yes, the histogram looks approximately normal even though the sample sizes are too small.
*** =hint
Since the tail of the distribution is on the right side, it is right-skewed. Type `results` to view the sample sizes in each racial group.
*** =pre_exercise_code
```{r}
library(HSAUR)
library(mosaic)
results <- favstats(schooldays$absent ~ schooldays$race)
hist(schooldays$absent)
```

*** =sct
```{r}
msg_bad <- "That is not correct. The distribution is very right skewed but the sample sizes are large."
msg_success <- "Exactly!"
test_mc(correct = 2, feedback_msgs = c(msg_bad, msg_success, msg_bad, msg_bad))
```

\end{verbatim}